Mining Pre-Exposure Prophylaxis Trends \\ in Social Media

### 2016-08-08 IEEEtran/bare_conf.tex
Have review comments from Tim and Jane and Patrick, ready for final revision with Shannon

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
%\author{\IEEEauthorblockN{Michael Shell}
%\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
%Georgia Institute of Technology\\
%Atlanta, Georgia 30332--0250\\
%Email: http://www.michaelshell.org/contact.html}
%\and
%\IEEEauthorblockN{Homer Simpson}
%\IEEEauthorblockA{Twentieth Century Fox\\
%Springfield, USA\\
%Email: homer@thesimpsons.com}
%\and
%\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
%\IEEEauthorblockA{Starfleet Academy\\
%San Francisco, California 96678--2391\\
%Telephone: (800) 555--1212\\
%Fax: (888) 555--1212}}

@@

We trained a word2vec model, and queried for the top 10 word-vectors related to the term PrEP (Table~\ref{tbl:w2v}). We found several HIV/AIDS related events, WorldAIDSDay, HLM2016AIDS, ICASA2015, as well as the PrEP drug Truvada, and the term HIV. In addition, we found the acronym ART which refers to Anti-Retroviral Therapy. DoingIt, and OneConversation, are ongoing efforts led by the Center for Disease Control (CDC) to spread awareness and reduce the spread of HIV. NBHAAD is an organization that is committed to increasing awareness for HIV within the Black community. Nancy Reagan, who died in early 2016, was mentioned in conjunction with her efforts to combat HIV in the 1980's. Together these results show us a high-level view of the important components of the national PrEP conversation on Twitter over the collection period.

@@

Next we sought to identify some temporal trends in PrEP related trends. We used Dynamic Topic Modeling (DTM) to identify how certain topics change over time. We specified 10 topics and used each week's worth of tweets, over a 30 week period from the 47th week of 2015 to the 14th week of 2016, as our time points.

>>>>

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Patrick Breen}
\IEEEauthorblockA{Institute of Bioinformatics\\
University of Georgia\\
Athens, Georgia\\
Email: pbreen@uga.edu}
\and
\IEEEauthorblockN{Jane Kelly}
\IEEEauthorblockA{ Georgia Department of \\Public Health\\
Atlanta, Georgia\\
Email: Jane.Kelly@dph.ga.gov}
\and
\IEEEauthorblockN{Timothy Heckman}
\IEEEauthorblockA{College of Public Health\\
University of Georgia\\
Athens, Georgia\\
Email: heckman@uga.edu}
\and
\IEEEauthorblockN{Shannon Quinn}
\IEEEauthorblockA{Department of \\Computer Science\\
University of Georgia\\
Athens, Georgia\\
Email: squinn@cs.uga.edu}
}
%\IEEEauthorblockN{Homer Simpson}
%\IEEEauthorblockA{Twentieth Century Fox\\
%Springfield, USA\\
%Email: homer@thesimpsons.com}
%\and
%\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
%\IEEEauthorblockA{Starfleet Academy\\
%San Francisco, California 96678--2391\\
%Telephone: (800) 555--1212\\
%Fax: (888) 555--1212}}

@@

We trained a word2vec model on the filtered dataset of 624,569 tweets, and queried for the top 10 word-vectors related to the term PrEP (Table~\ref{tbl:w2v}). We found several HIV/AIDS related events, WorldAIDSDay, HLM2016AIDS, ICASA2015, as well as the PrEP drug Truvada, and the term HIV. In addition, we found the acronym ART which refers to Anti-Retroviral Therapy. DoingIt, and OneConversation, are ongoing efforts led by the Center for Disease Control (CDC) to spread awareness and reduce the spread of HIV. NBHAAD is an organization that is committed to increasing awareness for HIV within the Black community. Nancy Reagan, who died in early 2016, was mentioned in conjunction with her efforts to combat HIV in the 1980's. Together these results show us a high-level view of the important components of the national PrEP conversation on Twitter over the collection period.

@@

Next we sought to identify some temporal trends in PrEP related trends. We used Dynamic Topic Modeling (DTM) on our tweet corpus to identify how certain topics change over time. We specified 10 topics and used each week's worth of tweets, over a 30 week period from the 47th week of 2015 to the 14th week of 2016, as our time points.
